Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-05 Cost_manuscript.Rmd
within-subj results edited. now onto computational modeling

  Next, we tested the hypothesis that foragers would display consistent and stable choices. Participants were deemed consistent if they did not quit during the handling time. To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time. Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code). Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed. These response time observations suggest clarity in participant preferences.

@@

  Stability was defined as a persistence in acceptance patterns throughout the experimental session. The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break. Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups. Figure 6 (left) shows that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in in line with reports where value is discounted as the length of the required effort increases (Treadway et al, 2009). We replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right). Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.

@@

  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should be robust to the ability to obtain the same rewards through different demands. We investigated this possibility by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments). We refer to observations from each block's wait trials by their effort pair (i.e. "Wait-C" for cognitive, and "Wait-P" for physical). We hypothesized that reward decision patterns would match those of the previous experiment, and that interleaving effort and delay would produce persistent preferences for wait trials.

@@

historyCoeffs_wth <- round(summary(historySize_wth[[historyIndex_wth]])$coefficients, digits = 2)

@@

  Analyses from the previous experiment were repurposed to examine cost differences within individuals. A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std. Error"]`, *p* `r report_p(historyCoeffs_wth["Offer", "Pr(>|z|)"])`), and that participants became more selective if they had recently observed large offers ($\beta$ = `r historyCoeffs_wth["recentOffers", "Estimate"]`, SE = `r historyCoeffs_wth["recentOffers", "Std. Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`). Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r AIC(historySize_wth[[historyIndex_wth]])`. However, this time participants were unaffected by recent reward misses (*p* > 0.05).
  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`). When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05). Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`). These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.

@@

  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones. As can be seen on Figure 8B, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 4A), differences among cost conditions were less evident. Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand. We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons). The model confirmed that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`). As in the previous section, pairwise comparison results are shown on the matrix in Figure 8C. This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions. The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`). This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.

```{r Earnings, prop completed, ME plots (Fig. 8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}

@@

  We then repeated the model comparison approach from the between-subject section, evaluating models ranging in complexity from intercept-only to a two-way interaction between cost and reward. Even though the a priori model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D). An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`). However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r round(mixLogis_compare$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`). (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally? Can't wrap my head around that yet, so this conclusion is pending**)

@@

  We next examined the stability in people's choices. If the cost of a particular demand was intrinsic, then its effect on choices should have been consistent as participants explored alternative costs. We started by examining whether individuals regreted engaging in a particular offer. Participants could quit either during the offer period (2 s) or during the handling time (10 s), allowing for a total of 12 seconds to give up on the current trial. The survival curve on Figure 9A shows quitting instances within trials for all participants. Censored points signal completions (at end of interval) and forced travels (throughout the trial). Similar to before, the survival analysis suggests that participants made most of their choices quickly within the offer window. In fact, the mean percentage of quits during the handling time was `r round(mean(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time. Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 9B). Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (mean = `r round(mean(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (mean = `r round(mean(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions. Similar to the between-subjects experiment, these results suggest that decision makers were confident in their adopted strategies, and were able to perform the tasks well.

@@

  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10). The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05). Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A). Mixed effects logistic regressions on each half separately confirmed this observation. The matrix on Figure 10 shows the coefficient magnitude for all pairwise comparisons among costs (computed by rotating the reference cost condition in the model), with crosses signaling non-significant coefficients (*p* > 0.05). This plot shows that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).

>>>>

  Next, we tested the hypothesis that foragers would display consistent and stable choices. Participants were deemed consistent if they did not quit after engaging in a trial. To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time. Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code). Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed. These response time observations suggest clarity in participant choices

@@

  Stability was defined as a persistence in acceptance patterns throughout the experimental session. The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break. Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups. Figure 6 (left) shows that the reduction acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands (Treadway et al, 2009). We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right). Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.

@@

  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should be robust to the ability to obtain the same rewards through different demands. We investigated this possibility by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments). We refer to observations from each block's wait trials by their effort pair (i.e. "Wait-C" for cognitive, and "Wait-P" for physical). We hypothesized that 1) reward decision patterns would match those of the previous experiment, and 2) that interleaving effort and delay would produce persistent preferences for wait trials.

@@

historyCoeffs_wth <- round(summary(historySize_wth[[historyIndex_wth]])$coefficients, digits = 3)

@@

  Analyses from the previous experiment were repurposed to examine cost differences within individuals. A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std. Error"]`, *p* `r report_p(historyCoeffs_wth["Offer", "Pr(>|z|)"])`), and that participants became more selective if they had recently observed large offers ($\beta$ = `r historyCoeffs_wth["recentOffers", "Estimate"]`, SE = `r historyCoeffs_wth["recentOffers", "Std. Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`). Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]], digits = 2))`. However, this time participants were unaffected by recent reward misses (*p* > 0.05).
  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`). When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05). Despite this deviation, participants earned a similar total amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`). These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.

@@

```{r Earnings, prop completed, ME plots (Fig. 7), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions. Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}

@@

  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones. Even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 8B), differences among cost conditions were less evident. Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands. A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`). Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D). An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`). However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r round(mixLogis_compare$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`). (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally? Can't wrap my head around that yet, so this conclusion is pending**). These initial results defied our predictions, suggesting that the availability of alternative demands erases preferences among demands (rather than inverting them).

@@

  Similar to the between-subject results, a survival analysis displayed that participants made most of their choices quickly within the offer window (Figure 8A). The median percentage of quits during the handling time was `r round(median(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time. Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 8B). Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions. Similar to the between-subjects experiment, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.

@@

  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10). The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05). Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A). Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle). 
  All together, our findings show that the stable preferences for cognitive effort observed during single-demand foraging slowly fade if alternative demands are introduced. This points towards task-specific and outcome-independent features from cognitive tasks that can be recalibrated by new experiences.
